---
title: "Week 4 Quiz"
author: "Parco Sin"
date: "October 18, 2016"
output: pdf_document
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# load libraries
library(tidyverse)
library(psych)
library(haven)
library(apaTables)
library(dplyr)

```

# Relations among variables

Below are the correlations among the variables for all participants.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
analytic_data <- read_csv(file="analytic_data.csv")
analytic_data_nogender <- select(analytic_data, -gender)
apa.cor.table(analytic_data_nogender, filename="Table1.doc", table.number=1)

```

## Relations among variables of men over 40

Below are the correlations among variables of men over 40 years of age.

```{r,echo=FALSE,message=FALSE, warning=FALSE}


analytic_data_men40 <- filter(analytic_data, gender=="Males") %>% filter(age>40)
analytic_data_men40 <- select(analytic_data_men40, -gender)
print(apa.cor.table(analytic_data_men40, filename="Table2.doc", table.number=2))
```

\pagebreak

#Relations among variables
##Scatter plot for Agreeableness and Extraversion

Below you can see the correlation between Agreeableness and Extraversion with a regression line. There is a positive correlation between the agreeableness and extraversion, r =.46.1, 95% CI [43.2, 49.0], p < .01. 

```{r,echo=FALSE,message=FALSE, warning=FALSE}
my.plot <- qplot(agreeableness, extraversion, data=analytic_data_men40)
my.plot <- my.plot + geom_smooth(method = "lm" , se = FALSE, color = "black")
my.plot <- my.plot + theme_classic(14)
my.plot <- my.plot + theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'black', size=0.5, linetype = 'solid'))
my.plot <- my.plot + labs(title="", x="Agreeableness", y="Extraversion")


print(my.plot)
ggsave("Figure1.pdf", plot=my.plot, width=6,height=6)
```

