---
title: 'Quiz'
author: "Parco Sin"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
  html_document:
    toc_depth: '3'
  word_document:
    toc_depth: '3'
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# load libraries
library(tidyverse)
library(psych)
library(haven)
library(apaTables)
library(dplyr)

```

# Relations among variables

Below are the correlations among the variables for all participants.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Load Data
bfi_data <- psych::bfi

#Labelling Data
categorical_variables <- select(bfi_data, gender, education, age)
categorical_variables$gender <- as.factor(categorical_variables$gender)
levels(categorical_variables$gender) <- list("Males"=1, "Females"=2)

#Creating Item Scales
agreeableness <- select (bfi_data, A1, A2, A3, A4, A5)
extraversion <- select (bfi_data, E1, E2, E3, E4, E5)
neuroticism <- select (bfi_data, N1, N2, N3, N4, N5)

#Reversing Items
agreeableness <- mutate(agreeableness, A1=7-A1)
extraversion <- mutate(extraversion, E1=7-E1)
extraversion <- mutate(extraversion, E2=7-E2)

#Fixing Bad Values
is_bad_value <- agreeableness<0 | agreeableness>6
agreeableness[is_bad_value] <- NA
is_bad_value <- extraversion<0 | extraversion >6
extraversion[is_bad_value] <- NA
is_bad_value <- neuroticism<0 |  neuroticism >6
neuroticism[is_bad_value] <- NA

#Obtaining Scale Scores
agreeableness <- psych::alpha(as.data.frame(agreeableness), check.keys=FALSE)$scores
extraversion <- psych::alpha(as.data.frame(extraversion), check.keys=FALSE)$scores
neuroticism <- psych::alpha(as.data.frame(neuroticism), check.keys=FALSE)$scores

#Combine into analytic_data
analytic_data <- cbind(agreeableness, extraversion, neuroticism, categorical_variables)
save(analytic_data,file="analytic_data.csv")

#### PART 2: CONDUCT ANALYSES ####
# 1 Correlation Tables
analytic_data_nogender <- select(analytic_data, -gender)
apa.cor.table(analytic_data_nogender, filename="Table1.doc", table.number=1)

```

## Relations among variables of men over 40

Below are the correlations among variables of men over 40 years of age.

```{r,echo=FALSE,message=FALSE, warning=FALSE}


analytic_data_men40 <- filter(analytic_data, gender=="Males") %>% filter(age>40)
analytic_data_men40 <- select(analytic_data_men40, -gender)
print(apa.cor.table(analytic_data_men40, filename="Table2.doc", table.number=2))
```

\pagebreak

#Relations among variables
##Scatter plot for Agreeableness and Extraversion

Below you can see the correlation between Agreeableness and Extraversion with a regression line. There is a positive correlation between the agreeableness and extraversion, r =.46.1, 95% CI [43.2, 49.0], p < .01. 

```{r,echo=FALSE,message=FALSE, warning=FALSE}
my.plot <- qplot(agreeableness, extraversion, data=analytic_data_men40)
my.plot <- my.plot + geom_smooth(method = "lm" , se = FALSE, color = "black")
my.plot <- my.plot + theme_classic(14)
my.plot <- my.plot + theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'black', size=0.5, linetype = 'solid'))
my.plot <- my.plot + labs(title="", x="Agreeableness", y="Extraversion")


print(my.plot)
ggsave("Figure1.pdf", plot=my.plot, width=6,height=6)
```

